Practical Optional Types for Clojure

### 2015-02-24 formal-model.tex
don't footnote size the last 3 pages!

The essential piece of occurrence typing's logical system is L-Update.
(The metavariable \propisnotmeta{} ranges over \t{} and \nottype{\t{}} (without variables).)

@@

This is where we combine propositions with similar objects
to learn new facts.
The full definition of \updateliteral{} is given
in

\begin{figure*}
  $$
\begin{array}{lllll}
\updatefigure
\end{array}
$$
\caption{Type Update}
\end{figure*}

@@

{\convertjavatypefigure{figure}{\footnotesize}}

\begin{figure}
  $$
\begin{array}{lllll}
  \restrictremovefigure{}
\end{array}
  $$
  \caption{Restrict and Remove}
\end{figure}

>>>>

The essential piece of occurrence typing's logical system is L-Update,
where we combine propositions that have similar objects to learn new facts.
(The metavariable \propisnotmeta{} ranges over \t{} and \nottype{\t{}} (without variables).)

@@

For example, if \inpropenv {\propenv{}} {\isprop {\Union{\Keyword}{\Nil}} {\x{}}}
and
\inpropenv {\propenv{}} {\notprop {\Nil{}} {\x{}}},
then
$$
\inpropenv {\propenv{}} {\isprop {\update {\Union{\Keyword}{\Nil}} {\nottype{\Nil{}}} {\emptypath{}}} {\x{}}},
$$
so we learn \inpropenv {\propenv{}} {\isprop {\Keyword{}} {\x{}}} using \removeliteral{} (figure~\ref{main:figure:restrictremove}).

Now that we have our path elements \classpe{} and \keype{\k{}}
and the typings rules that introduce them, we look at \updateliteral{} 
(figure~\ref{main:figure:update}) and give one interesting example for each.

\smallsection{\classpe{}}
If \inpropenv {\propenv{}} {\isprop {\Union{\Keyword}{\Nil}} {\x{}}}
and
\inpropenv {\propenv{}} {\isprop {\Value{\Keyword}} {\path{\classpe{}}{\x{}}}}

\smallsection{\keype{\k{}}}

\smallsection{Combination}

\begin{figure*}
  $$
\begin{array}{lllll}
\updatefigure
\end{array}
$$
\caption{Type Update}
\label{main:figure:update}
\end{figure*}

@@

{\convertjavatypefigure{figure}{\footnotesize}}
}

\begin{figure}
  $$
\begin{array}{lllll}
  \restrictremovefigure{}
\end{array}
  $$
  \caption{Restrict and Remove}
  \label{main:figure:restrictremove}
\end{figure}
